### 2018-01-11 master/paper.tex
Add tables and update related work

The proposed framework is a component-based framework for running mruby programs.
mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
Software can be developed using CBD with mruby on TECS.
In addition to supporting multitasking and co-routines, the mruby on TECS framework can be utilized RTOS functionalities such as periodic tasks and semaphores and supports legacy code such as a motor driver.

@@

The proposed framework, TINET+TECS, can configure the TCP/IP protocol stack with minimum set compared to the other platforms.
TINET+TECS improves configurability more than TINET and is suitable for embedded systems with memory constraint.

%6
\chapter{Conclusion}
\label{sec:Conclusion}

>>>>

Table \ref{tab:Scripting} compares the proposed framework to previous work.
The proposed framework is a component-based framework for running mruby programs.
mruby programs on TECS can be executed approximately 100 times faster than standard mruby programs.
Software can be developed using CBD with mruby on TECS.
In addition to supporting multitasking and co-routines, the mruby on TECS framework can be utilized RTOS functionalities such as periodic tasks and semaphores and supports legacy code such as a motor driver.

\begin{table*}[t]
    \caption{Comparison of open-source scripting Languages for embedded systems}
    \label{tab:Scripting}
    \centering
    {\small \tabcolsep = 1mm
    \begin{tabular}{c||cccccc}
        \hline\hline
        & \shortstack{Call\\C functions} 
        & \shortstack{Legacy code of\\embedded system} 
        & \shortstack{Multitasking} 
        & \shortstack{Co-routines}
        & \shortstack{RTOS\\functionalities} \\ \hline
        ChaiScript \cite{url:ChaiScript}              &            &            &            &              &              \\
        python-on-a-chip \cite{url:python-on-a-chip}  &            &            &            & green thread &              \\
        Owl system \cite{par:owl}                     & \checkmark & Partially  &            & green thread &              \\
        eLua \cite{url:eLua}                          & \checkmark & Partially  &            & \checkmark   &              \\
        Squirrel \cite{url:Squirrel}                  & \checkmark &            &            & \checkmark   &              \\
        mruby \cite{par:mruby}                        & \checkmark &            &            & \checkmark   &              \\
        Proposed framework                            & \checkmark & \checkmark & \checkmark & \checkmark   & \checkmark   \\
    \end{tabular}
    }
\end{table*}

@@

Table \ref{tab:TCP/IP} shows a comparison of TINET+TECS and previous work.
Note that the proposed framework, TINET+TECS, has demonstrated all features shown in Table \ref{tab:TCP/IP}.
TINET+TECS improves configurability more than TINET and is suitable for embedded systems with memory constraint.
The proposed framework, TINET+TECS, can configure the TCP/IP protocol stack with minimum set compared to the other platforms.

\begin{table*}[t]
    \caption{Comparison of open-source TCP/IP protocol stacks for embedded systems}
    \label{tab:TCP/IP}
    \centering
    {\small \tabcolsep = 1mm
    \begin{tabular}{c||ccccccc}
        \hline\hline
        & \shortstack{Configurability}
        & \shortstack{Generation} 
        & \shortstack{Binding} 
        & \shortstack{Support CBD} 
        & \shortstack{Memory saving} \\ \hline
        uIP \cite{par:uIP}     & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
        lwIP \cite{par:lwIP}   & $\bigtriangleup$          & Dynamic    & Dynamic  &              & \checkmark \\
        TINET \cite{url:TINET} &            & Static     & Dynamic  &              & \checkmark \\
        Proposed framework     & \checkmark & Static     & Dynamic  & \checkmark   & \checkmark \\
    \end{tabular}
    }
\end{table*}

%6
\chapter{Conclusions}
\label{sec:Conclusion}
